A* with Fast and Tight Heuristic in Road Networks

### 2020-08-13 paper/ch_potentials.tex
change queue column label to fix tab 2 width

\begin{table}
\centering
\caption{Query performance with different heuristics and optimizations on OSM Ger with $w_q = 1.05 \cdot w_\ell$.}\label{tab:building_blocks}
\input{table/building_blocks.tex}
\end{table}

>>>>

\begin{table}
\centering
\caption{Average query running times and number of queue pushs with different heuristics and optimizations on OSM Ger with $w_q = 1.05 \cdot w_\ell$.}\label{tab:building_blocks}
\input{table/building_blocks.tex}
\end{table}
